HBCC - DLPFC - FEATURECOUNTS - GRCh38 - CQN

### 2020-05-19 individual-cohorts/HBCC_DLPFC_FEATURECOUNTS_GRCh38_CQN.Rmd
rm individual id as random effect to debug

#### Phase I (clinical, ancestry and sample specific technical variables)
```{r phase1}
#Fit a base model with the following covariates
base_covars <- "Dx"
random_effect <- "Individual_ID"

# Set base formula
base_formula <- glue::glue("~ ", glue::glue_collapse(base_covars, sep = " + ")) %>%
  glue::glue(" + (1|{random_effect})")

>>>>

#### Phase I (clinical, ancestry and sample specific technical variables)
```{r phase1}
#Fit a base model with the following covariates
base_covars <- "Dx"

# Set base formula
base_formula <- glue::glue("~ ", glue::glue_collapse(base_covars, sep = " + "))
